---
title: "Congressional Committee Data Wrangling"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
# Load libraries here
library(readr)
library(here)
library(dplyr)
library(tidyverse)
library(stringr)
library(statnet)
library(networkD3)
```


## Loading the data

```{r}
committee_membership_current <- read_csv(here("Congressional Committee Shiny/committee-membership-current.csv"))

committees_current <- read_csv(here("Congressional Committee Shiny/committees-current.csv"))
```

## Make the column with the key in committees_current
- Otherwise I will not be able to link the names of the committees

```{r}
committees_current2 <- committees_current %>%
  mutate(key = paste(thomas_id, sub_thomas_id, sep = "")) %>%
  mutate(key = str_replace_all(key, 
                               "NA",
                               ""))
```

## Join the dataframes together by the key! :)

```{r}
committees_current2 <- committees_current2 %>%
  select(name, sub_name, key, type) %>%
  rename(com_name = name)

committees <- left_join(committee_membership_current, committees_current2, by = c("thomas_id" = "key"))
```


## Set up the "edge list"

```{r}
congressperson <- committees %>%
  distinct(name) %>%
  rename(label = name)

committee_names <- committees %>%
  distinct(thomas_id) %>%
  rowid_to_column("id")

committee_nodes <- committees %>%
  select(name, thomas_id) %>%
  arrange(name)

nodes <- left_join(committee_nodes, committee_names, by = "thomas_id") %>%
  select(-thomas_id) %>%
  rename(committee = id)

node_list <- nodes %>%
  distinct(name, .keep_all = TRUE) %>%
  rowid_to_column("id") %>%
  select(-committee)

write_csv(node_list, file = "node_list.csv")
```

## Get affiliation data for gender

```{r}
one16 <- read_csv("116_cong.csv")
one16 <- one16 %>%
  rename(name = officialFullName)

congressperson_affiliation <- congressperson %>%
  arrange(label) %>%
  rowid_to_column("id")
  
congressperson_gender <- left_join(congressperson_affiliation, one16, by = c("label" = "name"))

gender <- read_csv("gender.csv")

gender <- gender %>%
  mutate(gender = case_when(gender == 'M' ~ 0,
                            gender == 'F' ~ 1))

congressperson_affiliation <- inner_join(congressperson_affiliation, gender, by = "id")

gender_color <- gender %>%
  mutate(gender = case_when(gender == 0 ~ "blue",
                            gender == 1 ~ "pink2"))

congressperson_affiliation <- inner_join(congressperson_affiliation, gender_color, by = "id")

congressperson_affiliation <- congressperson_affiliation %>%
  select(-label.x, - label.y, -label)
```

## Adding the rest of the affilation data, besides gender, to the affilation dataframe

```{r}
# Join from committees: party, rank, chamber (saved as "type" in committees_current), leadership (title)

# Will not be making a color vector for this one, as we will FILTER the dataset to only include what the user inputs using this dataframe :)
committees_chamber <- committees %>%
  drop_na(type) %>%
  distinct(name, .keep_all = TRUE) %>%
  full_join(congressperson1, by = c("name" = "label")) %>%
  select(type, id)

congressperson_affiliation <- inner_join(congressperson_affiliation, committees_chamber, by = "id")

# Side note: majority is Republican
committees_party <- committees %>%
  full_join(congressperson1, by = c("name" = "label")) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(id, party) %>%
  mutate(party = case_when(party == "majority" ~ 0,
                           party == "minority" ~ 1))

congressperson_affiliation <- inner_join(congressperson_affiliation, committees_party, by = "id")

committees_party_colors <- committees_party %>%
  mutate(party = case_when(party == 0 ~ "red",
                           party == 1 ~ "blue"))

congressperson_affiliation <- inner_join(congressperson_affiliation, committees_party_colors, by = "id")

committees_leadership <- committees %>%
  full_join(congressperson1, by = c("name" = "label")) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(name, id, title) %>%
  mutate(title = case_when(title %in% c("Chair", "Ranking Member") ~ 1,
                           is.na(title) == TRUE ~ 0))

congressperson_affiliation <- inner_join(congressperson_affiliation, committees_leadership, by = "id")

committees_leadership_colors <- committees_leadership %>%
  mutate(title = case_when(title == 1 ~ "purple",
                           title == 0 ~ "gray"))

congressperson_affiliation <- inner_join(congressperson_affiliation, committees_leadership_colors, by = "id")

congressperson_affiliation <- congressperson_affiliation %>%
  select(-name.y) %>%
  rename(party_bin = party.x,
         party_color = party.y,
         title_bin = title.x,
         title_color = title.y,
         gender_bin = gender.x,
         gender_color = gender.y,
         name = name.x) %>%
  mutate(type = case_when(type == "house" ~ "House",
                          type %in% c("senate", "joint") ~ "Senate"))

congressperson_affiliation_labels <- congressperson_affiliation %>%
  select(gender_bin, type, party_bin, name, title_bin) %>%
  mutate(gender_bin = case_when(gender_bin == 1 ~ "Woman",
                                gender_bin == 0 ~ "Man"),
         party_bin = case_when(party_bin == 1 ~ "Democrat",
                               party_bin == 0 ~ "Republican"),
         title_bin = case_when((party_bin == "Democrat" & title_bin == 1) ~ "Ranking Member",
                               (party_bin == "Republican" & title_bin == 1) ~ "Committee Chair",
                               (title_bin == 0) ~ "No Leadership Position")) %>%
  rename(Gender = gender_bin,
         Chamber = type,
         Political_Party = party_bin,
         Name = name,
         Leadership_Position = title_bin) %>%
  select(Name, everything()) %>%
  arrange(Name)

# ROBIN USE THIS CODE TO CONVERT THE ROW IN THE DATAFRAME TO A VECTOR TO USE IN THE GRAPHY GRAPH
leadership_colors <- congressperson_affiliation[['title_color']]
```

## Write to a csv (for the app)
```{r, eval = FALSE}
write_csv(nodes, file = "committee_edge_list.csv")
write_csv(congressperson_affiliation, file = "congressperson_affiliation.csv")
```


## Turn it into a two mode network! (using `statnet`)
```{r}
com <- read.csv("committee_edge_list.csv", 
                #directed = FALSE,
                skip = 1,
                header = FALSE)

# With the four line script, below, we are saving all the unique names from the first column (first mode) into an object called “mode1”, and all the unique names from the second column (second mode) into an object called “mode2”
mode1 <- unique(com[,1])
mode2 <- unique(com[,2])
length(mode1)
## 479
length(mode2)
## 215

net <- as.network(com, 
                  bipartite=215,   # Number of nodes in the second mode (events)
                  directed=FALSE)

# Static plot of the network
gplot(net, usearrows = FALSE)
```


## Split it into one-mode networks for the purpose of graphing + finding centrality measures (who holds power more significantly + why???). Can I graph the thing below?? hm

```{r}
bipartite_matrix <- as.matrix(net)

#t(bipartite_matrix)

matrix_prod <- bipartite_matrix %*% t(bipartite_matrix)

diag(matrix_prod) <- 0

matrix_prod

net2 <- as.network(matrix_prod, directed = FALSE)

# Will have to experiment with vertex.col to get this hecking thing to graph colors by my affiliation data

# edge.lwd changes the thickness of the edges by the number of them
gplot(matrix_prod, vertex.col = leadership_colors, thresh = 1, jitter = TRUE, usearrows = FALSE, vertex.cex = 2)

```

## Centrality measures in `statnet`

```{r}
# First we need to binarize the network

library(ade4) # If you have not already done so

# I have a bipartite_matrix and net!
bipartite_matrix <- as.matrix(net)  # Extract the matrix

congressperson_jaccard <- dist.binary(t(bipartite_matrix), 
                                      method=1, upper=TRUE, 
                                      diag = FALSE) 

congressperson_jaccard <- as.matrix(congressperson_jaccard)   
diag(congressperson_jaccard) <- 0

# Binarize
congressperson_jaccard <- ifelse(congressperson_jaccard > 0.95, 1, 0)     

# Create a statnet network
jacc_congressperson <- as.network(congressperson_jaccard,    
                                  directed = FALSE)
gplot(jacc_congressperson,
      usearrows = FALSE, 
      jitter = TRUE,
      vertex.cex = 2)
```

```{r}
# Unsure why, but betweenness() and closeness() take a VERY long time to run/don't run D:
IDs <- jacc_congressperson%v%"vertex.names"
congress_deg  <- degree(jacc_congressperson)
#congress_bet  <- betweenness(jacc_congressperson)
#congress_clos <- closeness(jacc_congressperson,
           #             cmode="suminvdir")
congress_eig  <- evcent(jacc_congressperson)

congress_cent_df <- data.frame(IDs, 
                            congress_deg, 
                            #congress_bet, 
                            #congress_clos, 
                            congress_eig)

congress_cent_df

congressperson_affiliation2 <- inner_join(congressperson_affiliation, congress_cent_df, by = c("name" = "IDs"))

```


```{r}
# Hypothesis test:
t.test(congress_deg ~ party_bin, data = congressperson_affiliation2)
t.test(congress_eig ~ party_bin, data = congressperson_affiliation2)

# Save into dataframe; do this in the app for ease of printing
library(broom)
gender_deg <- tidy(t.test(congress_deg ~ gender_bin, data = congressperson_affiliation2))

# Definitely will also have to graph the results (boxplot of the centralization measures) so we know which one is higher :)
```

## Making the data for the interactive graph using `networkD3`

```{r}
# Make the matrix
m <- matrix_prod
idx = m > 0.001
edges = data.frame(
    source = row(m)[idx],
    target = col(m)[idx],
    corr = m[idx])

node_list
nodes_d3 <- mutate(congressperson_affiliation, id = id - 1)
edges_d3 <- mutate(edges, source = source - 1, target = target - 1)

ColourScale <- 'd3.scaleOrdinal()
            .domain(["blue", "pink2"])
           .range(["blue", "pink"]);'

forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "source", Target = "target", 
             NodeID = "name", Group = "gender_color", Value = "corr", 
             opacity = 1, fontSize = 16, zoom = TRUE, colourScale = JS(ColourScale))
```

